Extending Morphological Chains with Supervised Learning and Cross-Language Features

### 2015-12-10 paper/paper.tex
more citation stuff

Since a parent word can have multiple children (e.g., \emph{play} $\rightarrow$ \emph{plays} and \emph{play} $\rightarrow$ \emph{played}), words can be part of multiple chains. Thus multiple chains can share segments. Narasimhan makes use of this shared information by constructing a model which analyzes parent-child pairs.

@@

In the unsupervised version of our model, we observe words in a wordlist with their word count of occurrences. Additionally, we have access to a large corpus of text from which we can obtain semantic information. Our objective is to generate morphological segmentations, which we do by generating morphological chains, as given by Narasimhan et al.

@@

Additionally, we extend our feature set to include whether or not each candidate was
generated by a turkish translation (a strong indicator for parent-ness) and how confident
the Turkish model was in selecting a parent.

@@

\begin{table*}
    \begin{center}
        \begin{tabular}{ | l | l | l | l | l |}
            \hline
            Language & Method & Precision & Recall & F1 \\ \hline
                     & Narasimhan & 0.807 & 0.722 & 0.762 \\ 
                     & Unsupervised & -  & - & - \\ 
            English & Semi-supervised & - & - & - \\ 
                    & Two language unsupervised & - & - & - \\ 
                    & Two language semi-supervised & - & - & - \\ \hline
                    & Narasimhan & 0.743 & 0.520 & 0.612 \\ 
                    & Unsupervised & - & - & - \\ 
            Turkish & Semi-supervised & - & - & -  \\ 
                    & Two language unsupervised  & - & - & -  \\ 
                    & Two language semi-supervised  & - & - & -  \\ \hline
        \end{tabular}
        \caption{Results 'n shit TODO}
    \end{center}
\end{table*}

\begin{table*}
    \begin{center}
        \begin{tabular}{ | l | l | l | l | l | l |}
            \hline
            Language & \multicolumn{2}{|c|}{\textbf{Correct Segmentations}} & \multicolumn{3}{|c|}{\textbf{Incorrect Segmentations}}\\ \hline
                     & Word & Segmentation & Word & Predicted & Correct\\ \hline
            English & suburbanite & suburb/an/ite & provokingly & provok/ing/ly & provoking/ly  \\ 
                    & buffeted & buffeted & -  & - & -\\ 
                    & ewers' &  ewer/s/' & - & - & -\\ 
                    & yowling & yowl/ing & - & -& - \\ 
                    & Two language semi-supervised & - & - & - & -\\ \hline
                    & Narasimhan & 0.743 & 0.520 & 0.612 & -\\ 
                    & Unsupervised & - & - & - & -\\ 
            Turkish & Semi-supervised & - & - & -  & -\\ 
                    & Two language unsupervised  & - & - & -  & -\\ 
                    & Two language semi-supervised  & - & - & -  & -\\ \hline
        \end{tabular}
        \caption{Results 'n shit TODO}
    \end{center}
\end{table*}

>>>>

Since a parent word can have multiple children (e.g., \emph{play} $\rightarrow$ \emph{plays} and \emph{play} $\rightarrow$ \emph{played}), words can be part of multiple chains. Thus multiple chains can share segments.
\citeauthor{Narasimhan15} makes use of this shared information by constructing a model which analyzes parent-child pairs.

@@

In the unsupervised version of our model, we observe words in a wordlist with their word count of occurrences. Additionally, we have access to a large corpus of text from which we can obtain semantic information. Our objective is to generate morphological segmentations, which we do by generating morphological chains, as given by \citeauthor{Narasimhan15}

@@

Additionally, we extend our feature set to include whether or not each candidate was
generated by a Turkish translation (a strong indicator for parent-ness) and how confident
the Turkish model was in selecting a parent.

@@

\begin{table*}
    \begin{center}
        \begin{tabular}{ | l | l | l | l | l |}
            \hline
            Language & Method & Precision & Recall & F1 \\ \hline
                     & \citeauthor{Narasimhan15} & 0.807 & 0.722 & 0.762 \\ 
                     & Unsupervised & -  & - & - \\ 
            English & Semi-supervised & - & - & - \\ 
                    & Two language unsupervised & - & - & - \\ 
                    & Two language semi-supervised & - & - & - \\ \hline
                    & \citeauthor{Narasimhan15} & 0.743 & 0.520 & 0.612 \\ 
                    & Unsupervised & - & - & - \\ 
            Turkish & Semi-supervised & - & - & -  \\ 
                    & Two language unsupervised  & - & - & -  \\ 
                    & Two language semi-supervised  & - & - & -  \\ \hline
        \end{tabular}
        \caption{Results 'n shit TODO}
    \end{center}
\end{table*}

\begin{table*}
    \begin{center}
        \begin{tabular}{ | l | l | l | l | l | l |}
            \hline
            Language & \multicolumn{2}{|c|}{\textbf{Correct Segmentations}} & \multicolumn{3}{|c|}{\textbf{Incorrect Segmentations}}\\ \hline
                     & Word & Segmentation & Word & Predicted & Correct\\ \hline
            English & suburbanite & suburb/an/ite & provokingly & provok/ing/ly & provoking/ly  \\ 
                    & buffeted & buffeted & -  & - & -\\ 
                    & ewers' &  ewer/s/' & - & - & -\\ 
                    & yowling & yowl/ing & - & -& - \\ 
                    & \citeauthor{Narasimhan15} & 0.743 & 0.520 & 0.612 & -\\ 
                    & Unsupervised & - & - & - & -\\ 
            Turkish & Semi-supervised & - & - & -  & -\\ 
                    & Two language unsupervised  & - & - & -  & -\\ 
                    & Two language semi-supervised  & - & - & -  & -\\ \hline
        \end{tabular}
        \caption{Results 'n shit TODO}
    \end{center}
\end{table*}
